Associative Data Structures for Website Filtering

### 2014-04-17 paper/paper.tex
wrote the abstract

\title{Data Structures Comparative Review Thing}
\author{Pieter Brederode, Timo Koppenberg, \\ Jelco Bodewes, Anton Golov}

@@

    \begin{abstract}
        We did research and got results~\cite{CallOfCthulhu}.
    \end{abstract}

>>>>

\title{Associative Data Structures for Website Filtering}
\author{Pieter Brederode, Timo Koppenberg, \\ Jelco Bodewes, Anton Golov}

@@

    \begin{abstract}
        In this paper, we will research associative data structures. This is done in the context of
        a website filter. We look at three different data structures, the hash map, binary search tree
        and the skip list. We insert keys of three different types, namely IP adress, domain name and
        full path URL. We judge the competency of our data strucutre based on insert time, query time
        and memory usage, inserting data sets of sizes $2^x$ for $8 \le x \le 20$. We describe the details
        of our research and the implementation using C++. The results are that hash maps are much faster
        than the other structures, where skip lists use the least memory and binary search trees are
        only useful with very few insertions of simple keys and more insertions than queries.
    \end{abstract}
